Title

### 2019-05-22 4_method.tex
more math

\subsection{Beading strategy}
\hl{This section needs to change and the changes will impact other sections as well.}
We need to change the method overview.
The transition placement needs to depend on the MAT distance transform function described below.

@@

For our application we define a $W$ adhereing to the following aditional constraints in order of priority:
\begin{itemize}
\item Minimize unfilled area
\item Try to get the outer bead width $W_1$ as close as possible to $\wout$
\item Have the rest of the $W_n$ the same width
\item at transition regions decide between $n$ and $n+1$ beads using the Loss fuction scheme below
\item From a $d$ for which $b(d) = 3$ we don't consider fractional $b(d)$ anymore; we don't allow singleton beads along the medial axis
\end{itemize}

@@

\begin{align}
L(w_1) &= 
  \begin{cases} 
%  \infty & \text{if } w < w_\text{min} \\
   (w - \wout) / (\wmax - \wout) & \text{if } w > \wout\\
   (\wout - w) / (\wout - \wmin)       & \text{otherwise}
  \end{cases}
  \\
L(w_n) &= 
  \begin{cases} 
%  \infty & \text{if } w < w_\text{min} \\
   (w - \win) / (\wmax - \win) & \text{if } w > \win\\
   (\win - w) / (\win - \wmin)       & \text{otherwise}
  \end{cases}
\\
L(W(d)) &= \sum_{n=1}^{n=\lceil f(d) \rceil} L( W(d)_n )
\end{align}

Together these prioritized constraints uniquely define a single $W$, depending on $\wmin, \wmax, \wout,\win$.
An example is given in \cref{transition_location}.

\begin{figure*}
\centering
\includegraphics[width=.9\textwidth]{sources/method/ticking_v2.pdf}
\includegraphics[width=.25\textwidth]{sources/method/transition_location_precise.pdf}
\caption{Mapping of different lengths to a ticking. Transition location on a line-line segment is to the right of the middle because the preferred line width is to the left of the middle in the range.}
\label{transition_location}
\end{figure*}

>>>>

\subsection{Beading strategy}
The next step is to determine how we will fill a given distance between the outline and a significant/marked MAT segment with a whole number of beads. We want to fit an exact whole number of beads in order to prevent a gap being generated.

@@

For our application we define a $W$ adhereing to the following aditional constraints in order of priority:
\begin{itemize}
\item Minimize unfilled area
\item Try to get the outer bead width $W_1$ as close as possible to $\wout$
\item Have the rest of the $W_n$ the same width
\item at transition regions decide between $n$ and $n+1$ beads using the Loss fuction scheme below
\item From a $d$ for which $b(d) = 3$ we don't consider fractional $b(d)$ anymore; we don't allow singleton beads along the medial axis.
\hl{Perhaps we should disallow this because that would require a different transition length}
\end{itemize}

@@

\begin{align}
L(w_1) &= 
  \begin{cases} 
%  \infty & \text{if } w < w_\text{min} \\
   (w - \wout) / (\wmax - \wout) & \text{if } w > \wout\\
   (\wout - w) / (\wout - \wmin)       & \text{otherwise}
  \end{cases}
  \\
L(w_n) &= 
  \begin{cases} 
%  \infty & \text{if } w < w_\text{min} \\
   (w - \win) / (\wmax - \win) & \text{if } w > \win\\
   (\win - w) / (\win - \wmin)       & \text{otherwise}
  \end{cases}
\\
L(W(d)) &= \left(b(d) - \lfloor b(d) \rfloor \right) L \left( W(d)_{\lceil b(d) \rceil} \right)  +  \sum_{n=1}^{n=\lfloor b(d) \rfloor} L( W(d)_n )
\end{align}

(Singular beads are counted only half.)
Together these prioritized constraints uniquely define a single $W$, depending on $\wmin, \wmax, \wout,\win$.
An example is given in \cref{transition_location}.

\begin{figure*}
\centering
\includegraphics[width=.9\textwidth]{sources/method/ticking_v2.pdf}
\caption{Mapping of different lengths to a ticking. Transition location on a line-line segment is to the right of the middle because the preferred line width is to the left of the middle in the range.}
\label{transition_location}
\end{figure*}

We introduce a function which produces the $d$ at which all widths are prefered: 
\begin{align}
p(n) =
  \begin{cases} 
   \frac12 \wout & \text{if } n = \frac12 \\
    \wout + (n - 1) \win       & \text{otherwise}
  \end{cases}
\end{align}
We call a distance $d$ `prefered' when $d = p(b(d))$

\subsubsection{MAT distance transform}
In order to apply the beading strategy to the MAT
we assign each node $v$ of the medial axis a bead quantity $B^*$ which is initially based on $b(R(v))$, but it is modified in order to prevent discontinuities and remaining gaps.

\hl{How should we define $B^*$? Currently it is always the rounded measure, but it needs to be unrounded in non-marked areas and it needs to support fractional numbers around transitions!}

The bead quantity measure $B^*$ measure should be rounded
where the MAT distance measure $R$ is a local maximum: when all directly connected nodes have a lower MAT distance measure.
See bottom of \cref{rounded_vs_unrounded}.
